Post-Disturbance Tree Community Trajectories in a Neotropical Forest

### 2018-04-19 WholePlotTrajectories.Rmd
Graphslegend
Webpages

---
title: "Post-Disturbance Tree Community Trajectories in a Neotropical Forest"
author:
  - name: Ariane MIRABEL
    authsuperscript: 1*
  - name: Eric Marcon
    authsuperscript: 1
  - name: Bruno Hérault
    authsuperscript: 2 3
affiliation:
  - affsuperscript: 1
    dptuniv: UMR EcoFoG, AgroParistech, CNRS, Cirad, INRA, Université des Antilles, Université de Guyane.
    address: >
      Campus Agronomique,
      97310 Kourou,
      France.
  - affsuperscript: 2
    dptuniv: Cirad, Univ montpellier, UR Forests & Societies.
    address: >
      Montpellier,
      France.
  - affsuperscript: 3
    dptuniv: INPHB, Institut National Polytechnique Félix Houphouet-Boigny
    address: >
      Yamoussoukro,
      Ivory Coast.
corrauthor:
    email: ariane.mirabel@ecofog.gf
    url: http://www.ecofog.gf/spip.php?article47
abstract: >   #Pour avoir plusieurs lignes qui suivent. Commencer à 2 caractères
  Résumé de l'article.
keywords: [mot-clés, séparés par des virgules]
journalinfo: Hal xxx
archive: DOI xxxx
date: "`r format(Sys.time(), '%d %B %Y')`"
preamble: >
  \usepackage{textcomp}
  \DeclareUnicodeCharacter{B0}{\textdegree}
  \usepackage{tabu}
  \renewenvironment{table}{\begin{table*}}{\end{table*}\ignorespacesafterend}
  \hyphenation{bio-di-ver-si-ty sap-lings}
bibliography: references.bib
lang: english
keywordlabel: Keywords
corrauthorlabel: Corresponding author
output:
  bookdown::pdf_book:
    base_format: EcoFoG::article
    keep_tex: TRUE
  bookdown::gitbook: default
  bookdown::word_document2: default
---

@@

CWMdraw(CWM)

@@

While for undisturbed plots the Richness, Shannon and Simpson diversity remained comparable to the values in 1989, the trajectories of all disturbed plots showed significant increase positively correlated with the disturbance intensity ($\rho_{spearman}^{Shannon}=0.87$, and $\rho_{spearman}^{Simpson}=0.88$) (Figure \@ref(fig:DivTaxo)). 
The Richness was less affected by the initial disturbance except for the higher intensity (T3 plots) (Figure \@ref(fig:DivTaxo)). 
The Shannon and Simpson diversities however first significantly increased, illustrating an increasing evenness, before reaching a maximum around 15 years after disturbance for all plots except one from T1 treatment and one from T2 treatment (Figure \@ref(fig:DivTaxo)).

@@

For all undisturbed plots the Rao diversity remained comparable to the values in 1989, the trajectories of all disturbed plots showed significant increase positively correlated with the disturbance intensity (Figure \@ref(fig:DivFun)). 
Although a first increase of plots functional diversity that was all the more important than initial disturbance was intense, 30 after disturbance the diversity was similar among disturbed plots and significantly higher than this of control plots.

@@

>>>>

---
title: "Post-Disturbance Tree Community Trajectories in a Neotropical Forest"
author:
  - name: Ariane MIRABEL
    authsuperscript: 1*
  - name: Eric Marcon
    authsuperscript: 1
  - name: Bruno Hérault
    authsuperscript: 2 3
affiliation:
  - affsuperscript: 1
    dptuniv: UMR EcoFoG, AgroParistech, CNRS, Cirad, INRA, Université des Antilles, Université de Guyane.
    address: >
      Campus Agronomique,
      97310 Kourou,
      France.
  - affsuperscript: 2
    dptuniv: Cirad, Univ montpellier, UR Forests & Societies.
    address: >
      Montpellier,
      France.
  - affsuperscript: 3
    dptuniv: INPHB, Institut National Polytechnique Félix Houphouet-Boigny
    address: >
      Yamoussoukro,
      Ivory Coast.
corrauthor:
    email: ariane.mirabel@ecofog.gf
    url: http://www.ecofog.gf/spip.php?article47
abstract: >   #Pour avoir plusieurs lignes qui suivent. Commencer à 2 caractères
  Résumé de l'article.
keywords: [mot-clés, séparés par des virgules]
journalinfo: Hal xxx
archive: DOI xxxx
date: "`r format(Sys.time(), '%d %B %Y')`"
preamble: >
  \usepackage{textcomp}
  \DeclareUnicodeCharacter{B0}{\textdegree}
  \usepackage{tabu}
  \renewenvironment{table}{\begin{table*}}{\end{table*}\ignorespacesafterend}
  \hyphenation{bio-di-ver-si-ty sap-lings}
bibliography: references.bib
lang: english
keywordlabel: Keywords
corrauthorlabel: Corresponding author
output:
  bookdown::gitbook: default
  bookdown::pdf_book:
    base_format: EcoFoG::article
    keep_tex: TRUE
  bookdown::word_document2: default
---

@@

CWMdraw(CWM)
legendCWM()

@@

For undisturbed plots the Richness, Shannon and Simpson diversity remained comparable to the initial values 5 years after disturbance.
After disturbance, the richness increased after low disturbance intensity, with a maximum increase of 14 botanical genuses (for plot 3 after treatment 2), but followed a unimodal decrease with a return to initial values after intense disturbance.
The taxonomic evenness (Shannon and Simpson diversities), however, significantly increased after all disturbance regime.
The evenness followed a unimodal trajectory with a just beginning return towards initial values and a maximum reached around 20 years and positively correlated to the disturbance intensity ($\rho_{spearman}^{Shannon}=0.92$, and $\rho_{spearman}^{Simpson}=0.97$).
Only two T3 plots, plots 8 and 12, remained increasing 30 years after disturbance \@ref(fig:DivTaxo)), suggesting a similar be much delayed unimodal trajectory.

@@

For all undisturbed plots the Rao diversity remained comparable to the initial values, 5 years after disturbance (1989 inventories).
The trajectories of all disturbed plots followed a unimodal trajectory with a maximum positively correlated to disturbance intensity ($\rho_{spearman}$) (Figure \@ref(fig:DivFun)). 
Thirty years after disturbance all plots, whenever the initial disturbance intensity, regained diversity values similar to their initial avule and to those of control plots.

@@

# Conclusions

### 2018-04-19 WholePlotTrajectories.tex
Graphslegend
Webpages

While for undisturbed plots the Richness, Shannon and Simpson diversity
remained comparable to the values in 1989, the trajectories of all
disturbed plots showed significant increase positively correlated with
the disturbance intensity (\(\rho_{spearman}^{Shannon}=0.87\), and
\(\rho_{spearman}^{Simpson}=0.88\)) (Figure \ref{fig:DivTaxo}). The
Richness was less affected by the initial disturbance except for the
higher intensity (T3 plots) (Figure \ref{fig:DivTaxo}). The Shannon and
Simpson diversities however first significantly increased, illustrating
an increasing evenness, before reaching a maximum around 15 years after
disturbance for all plots except one from T1 treatment and one from T2
treatment (Figure \ref{fig:DivTaxo}).

@@

For all undisturbed plots the Rao diversity remained comparable to the
values in 1989, the trajectories of all disturbed plots showed
significant increase positively correlated with the disturbance
intensity (Figure \ref{fig:DivFun}). Although a first increase of plots
functional diversity that was all the more important than initial
disturbance was intense, 30 after disturbance the diversity was similar
among disturbed plots and significantly higher than this of control
plots.

@@

>>>>

For undisturbed plots the Richness, Shannon and Simpson diversity
remained comparable to the initial values 5 years after disturbance.
After disturbance, the richness increased after low disturbance
intensity, with a maximum increase of 14 botanical genuses (for plot 3
after treatment 2), but followed a unimodal decrease with a return to
initial values after intense disturbance. The taxonomic evenness
(Shannon and Simpson diversities), however, significantly increased
after all disturbance regime. The evenness followed a unimodal
trajectory with a just beginning return towards initial values and a
maximum reached around 20 years and positively correlated to the
disturbance intensity (\(\rho_{spearman}^{Shannon}=0.92\), and
\(\rho_{spearman}^{Simpson}=0.97\)). Only two T3 plots, plots 8 and 12,
remained increasing 30 years after disturbance \ref{fig:DivTaxo}),
suggesting a similar be much delayed unimodal trajectory.

@@

For all undisturbed plots the Rao diversity remained comparable to the
initial values, 5 years after disturbance (1989 inventories). The
trajectories of all disturbed plots followed a unimodal trajectory with
a maximum positively correlated to disturbance intensity
(\(\rho_{spearman}\)) (Figure \ref{fig:DivFun}). Thirty years after
disturbance all plots, whenever the initial disturbance intensity,
regained diversity values similar to their initial avule and to those of
control plots.

@@

\section{Conclusions}\label{conclusions}
